N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
Section 3 is mostly done - I didn't talk about the repl, matrix or utils files very much. I'm going to start poking around with the Design Decision section now.

  As we touched on before - the notion of a game is generalized in the
  \texttt{game.sml} file. This defines the signatures and functor to run a game.
  The general pattern for a game under our model consists of three purposely
  isolated pieces.
  These are \textit{State}, \textit{Actions}, and \textit{Agents} which are
  each given their own signature in \texttt{game.sml}.
  These are then wrapped together with a functor. The idea is that any game
  consists of a state, a set of actions on that state, and an agents that take
  actions for a state. A specific implementation of a game would use the
  relationship between these three general pieces to define a runnable game with
  its own modules.

  Our implementation of \textit{Tic-tac-toe} uses this game model to operate and
  is primarily defined within \texttt{tictactoe.sml}.
  Here we have two signatures - one that extends state (the \texttt{STATE}
  signature from \texttt{game.sml}) for \textit{Tic-tac-toe}
  called \texttt{TTTSTATE} and another that does the same with action called
  \texttt{TTTACTION} - we don't extend the \texttt{AGENT} signature specifically
  for \textit{Tic-tac-toe}.

  There are many module structures instantiated here for the various kinds of
  state, actions and agents that we eventually want to use -
  such as \texttt{TttState} and \texttt{TttAction} for instance.
  These are bound to functors like \texttt{TttStateFn} which takes
  a module implementing a square matrix module (\texttt{SQUAREMATRIX})
  and returns a module that implements \texttt{TTTSTATE}.

@@

  The idea being that we instantiated specific module structures
  (like \texttt{TttState}) for different cases of actions and states that may
  occur in various kinds of \textit{Tic-tac-toe} games.
  We then described functors which linked these structures to the functions
  meant for that specific use and returned a new .
  When provided with the correct input module these functors will give us
  modules that implement that portion of the game pattern - which we then use
  with another structure and another functor for the next modular piece of the
  game.
  % ugh I should probably rewrite that last paragraph

>>>>

  As we touched on before - the notion of a game is generalized in the
  \texttt{game.sml} file. This defines the signatures which make up the pattern
  of a game and a functor to run a game.
  The general pattern for a game under our model consists of three purposely
  isolated pieces.
  These are \textit{State}, \textit{Actions}, and \textit{Agents} - which are
  each given their own signature in \texttt{game.sml}.
  These are then wrapped together with a functor to execute a game.
  The idea is that any game consists of a state, a set of actions on that state,
  and an agents that take actions for a state. A specific implementation of a
  game would use the relationship between these three general pieces to define
  a runnable game with its own modules.

  Our implementation of \textit{Tic-tac-toe} uses this game model to operate and
  is primarily defined within \texttt{tictactoe.sml}.
  This roughly follows the order:
  State $\rightarrow$ Action $\rightarrow$ Agent $\rightarrow$ Execution.

  In \texttt{tictactoe.sml} we have two signatures - one that extends state
  (the \texttt{STATE} signature from \texttt{game.sml}) for \textit{Tic-tac-toe}
  called \texttt{TTTSTATE} and another that does the same with action
  (the \texttt{ACTION} signature from \texttt{game.sml}) called
  \texttt{TTTACTION}.
  We don't extend the \texttt{AGENT} signature specifically for \textit{Tic-tac-toe}.

  There are many module structures instantiated in \texttt{tictactoe.sml}
  for the various kinds of state, actions and agents that we eventually want to
  use - such as \texttt{TttState} and \texttt{TttAction} for instance - but each will
  be used to implement the next kind of module.
  These module structures are bound to functors like \texttt{TttStateFn} which
  takes a module implementing a square matrix module (\texttt{SQUAREMATRIX})
  and returns a module that implements \texttt{TTTSTATE}.

@@

  The idea being that we instantiated specific module structures
  (like \texttt{TttState}) for different cases of states, actions and agents
  that may occur in various kinds of \textit{Tic-tac-toe} games.
  We then described functors which linked these structures to the functions
  meant for that specific use and returned a new module.
  When provided with the correct input module, these functors will give us
  modules that implement that portion of the overall game pattern.
